---
output: github_document
---

[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://img.shields.io/badge/repo%20status-concept-orange.svg)](http://www.repostatus.org/#concept)
[![Travis-CI Build Status](https://travis-ci.org/ropenscilabs/datasauce.svg?branch=master)](https://travis-ci.org/ropenscilabs/datasauce)



<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# datasauce

The goal of datasauce is to facilitate creation and manipulation of metadata which uses Google's [Structured Data](https://developers.google.com/search/docs/guides/intro-structured-data) format; essentially [JSON-LD](https://json-ld.org) formatted files which use <https://schema.org/Dataset>.  Users can check their document interactively using the [Structured Data Testing Tool](https://search.google.com/structured-data/testing-tool). ***See [Google's Dataset Documentation](https://developers.google.com/search/docs/data-types/dataset) for more on [this approach](https://ai.googleblog.com/2017/01/facilitating-discovery-of-public.html).***



The [rOpenSci Project](https://ropensci.org) may use `datasauce` to create and manage metadata 
about all of the open data sources that can be accessed with rOpenSci packages.  This could facilitate
discovery of relevant data.

## Installation

You can install `datasauce` from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ropenscilabs/datasauce")
```

## Getting Started

Concept design stage still.  Use `?` functions and tab completion to see slots of available objects.

```{r}
me <- Person(givenName = "Carl", familyName = "Boettiger", email = "cboettig@ropensci.org")
as_jsonld(me)
ds <- Dataset()
```
