---
output: github_document
---

[![Travis-CI Build Status](https://travis-ci.org/ropenscilabs/datasauce.svg?branch=master)](https://travis-ci.org/ropenscilabs/datasauce)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# datasauce

The goal of datasauce is to facilitate creation and manipulation of metadata which uses Google's [Structured Data](https://developers.google.com/search/docs/guides/intro-structured-data) format; essentially [JSON-LD](https://json-ld.org) formatted files which use <https://schema.org/Dataset>. (Support for extracting structured data from microdata and RDFa formats may be added later).

The [rOpenSci Project](https://ropensci.org) will be using datasauce to create and manage metadata 
about all of the open data sources that can be accessed with rOpenSci packages.  This should facilitate
discovery of relevant data.

## Installation

You can install datasauce from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ropenscilabs/datasauce")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```
